---
title: "Aim 2 - model fitting for casecrossover dlnm"
author: "Shreya Patel"
format: html
editor: visual
---

```{r}
#| echo: false
#| message: false # Removes messages
#| warning: false


library(kableExtra)
library(knitr)
library(lubridate)
library(dplyr)
library(tidyverse)
library(dlnm)
library(splines)
library(mvmeta)
library(survival)
library(data.table)

setwd("Y:/patels")
source("Y:/patels/Code/edvisits2.R")
source('Y:/patels/Code/casecrossv2.R')


```

# Case-crossover logistic regression model in a DLMN

-7 day lag, with 2 logknots, model adjusted for holidays

```{r}
#| echo: false
#| message: false # Removes messages
#-----------------------------------------------------------
# FUNCTION: run_dlnm_casecross
#-----------------------------------------------------------
run_dlnm_casecross_ns <- function(data,
                               temp_var = "temp.mean",
                               lag_days = 7,
                               exp_probs,
                               centering = "median"
                               ) 
  {
  
  #-------------------------------
  # Prepare exposure variable
  #-------------------------------
  temp <- data[[temp_var]]
  exp_knots <- quantile(temp, probs = exp_probs, na.rm = TRUE)
  perc <- quantile(temp, probs = c(0.90, 0.95, 0.975, 0.99), na.rm = TRUE)
  
  #-------------------------------
  # Define crossbasis
  #-------------------------------
  cb <- crossbasis(temp,
                   lag = lag_days,
                   argvar = list(fun = "ns", 
                                 knots = exp_knots),
                   arglag = list(fun = "ns", 
                                 knots = logknots(lag_days, 2)))
  
  #-------------------------------
  # Fit conditional logistic regression
  #-------------------------------
  
  model <- clogit(case ~ cb + holiday + strata(claim_id), data = data)
  
  #-------------------------------
  # Identify centering value (MMT)
  #-------------------------------
  if (centering == "median") {
    cen_temp <- median(temp, na.rm = TRUE)
  } else {
    cen_temp <- centering
  }
  
  #-------------------------------
  # Predict overall exposure-response and lag effects
  #-------------------------------
  cp_overall <- crosspred(cb, model,
                          cen = cen_temp,
                          at = seq(min(temp, na.rm = TRUE),
                                   max(temp, na.rm = TRUE),
                                   length = 100))
  
  cp_perc <- crosspred(cb, model,
                       cen = cen_temp,
                       at = perc,
                       bylag = 0.2)
  

  #-------------------------------
  # Plots
  #-------------------------------
  par(mfrow = c(1, 2), mar = c(5, 4, 4, 2) + 0.1)
  
  ## Exposure-response curve
  plot(cp_overall, "overall",
       col = 1,
       ylab = "OR",
       xlab = "Average Temperature (°F)",
       axes = TRUE,
       lwd = 1.5,
       log = "y",
       main = "Exposure-Response: Extreme Heat and ED Visits", cex.main = 0.8)
  abline(v = perc, col = "red", lty = 2)
  mtext(paste0("Ref = ", round(cen_temp, 1), "°F"), cex = 0.6)
  
  ## Lag-response at 90th percentile
  plot(cp_perc, "slices",
       var = as.numeric(perc["99%"]),
       col = 1,
       ylab = "OR",
       xlab = "Lag (days)",
       lwd = 1.5,
       main = paste0("Lag-Response (", round(perc["99%"], 1), "°F)"), cex.main = 0.8)
  mtext(paste0("Ref = ", round(cen_temp, 1), "°F"), cex = 0.6)
  

  
  #-------------------------------
  # Return summary
  #-------------------------------
 
# Save results as a dataframe
cumulativeRR <- data.frame(
  Knots = paste0("(", paste(round(exp_probs, 2), collapse = ", "), ")"),
  Percentile = names(perc),
  Temperature = round(as.numeric(perc),2),
  AIC = AIC(model),
  RR = round(cp_perc$allRRfit, 2),
  LowerCI = round(cp_perc$allRRlow, 2),
  UpperCI = round(cp_perc$allRRhigh, 2)
)

return(cumulativeRR)
}


```

## Results: All-cause antepartum and postpartum visits

```{r}
#| message: false # Removes messages



run_dlnm_casecross_ns(
  data = pregpp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90))

 run_dlnm_casecross_ns(
  data = pregpp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

run_dlnm_casecross_ns(
  data = pregpp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)
run_dlnm_casecross_ns(
  data = pregpp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)
run_dlnm_casecross_ns(
  data = pregpp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 



```

#### Knots at (0.33,0.66) has the lowest AIC

# Results: All-cause pregnancy visits

```{r}
#| message: false # Removes messages


 run_dlnm_casecross_ns(
  data = preg_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)

run_dlnm_casecross_ns(
  data = preg_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

 run_dlnm_casecross_ns(
  data = preg_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)


run_dlnm_casecross_ns(
  data = preg_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

run_dlnm_casecross_ns(
  data = preg_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
  )


```

#### Knots at (0.50,0.90) has the lowest AIC

# Postpartum

```{r}
#| message: false # Removes messages


 run_dlnm_casecross_ns(
  data = pp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)

run_dlnm_casecross_ns(
  data = pp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

run_dlnm_casecross_ns(
  data = pp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)


pp_knots_255075ns <- run_dlnm_casecross_ns(
  data = pp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 


run_dlnm_casecross_ns(
  data = pp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)

```

#### Knots at (0.33,0.66) has the lowest AIC

# Pregnancy-related ED visits

```{r}
#| message: false # Removes messages

run_dlnm_casecross_ns(
  data = pregrel_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)

run_dlnm_casecross_ns(
  data = pregrel_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

 run_dlnm_casecross_ns(
  data = pregrel_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)

 run_dlnm_casecross_ns(
  data = pregrel_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

run_dlnm_casecross_ns(
  data = pregrel_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)

```

#### Knots at (0.50,0.90) has the lowest AIC

# Mental Health related visits

```{r}
#| message: false

run_dlnm_casecross_ns(
  data = mental_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)

run_dlnm_casecross_ns(
  data = mental_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

run_dlnm_casecross_ns(
  data = mental_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)

 run_dlnm_casecross_ns(
  data = mental_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

 run_dlnm_casecross_ns(
  data = mental_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)

```

#### Knots at (0.50,0.90) has the lowest AIC

# Respiratory causes

```{r}
#| message: false # Removes messages


run_dlnm_casecross_ns(
  data = resp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)


 run_dlnm_casecross_ns(
  data = resp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)


run_dlnm_casecross_ns(
  data = resp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)


run_dlnm_casecross_ns(
  data = resp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

run_dlnm_casecross_ns(
  data = resp_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)


```

#### Knots at (0.50,0.90) has the lowest AIC

## Genitourinary causes

```{r}
#| message: false # Removes messages

run_dlnm_casecross_ns(
  data = genit_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90))

run_dlnm_casecross_ns(
  data = genit_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

run_dlnm_casecross_ns(
  data = genit_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)

run_dlnm_casecross_ns(
  data = genit_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

run_dlnm_casecross_ns(
  data = genit_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)


```

#### Knots at (0.50,0.90) has the lowest AIC

## inury causes

```{r}
#| message: false # Removes messages


 run_dlnm_casecross_ns(
  data = injury_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.50,0.90)
)

 run_dlnm_casecross_ns(
  data = injury_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.10,0.75)
)

 run_dlnm_casecross_ns(
  data = injury_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.75)
)

 run_dlnm_casecross_ns(
  data = injury_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.25,0.50,0.75)
) 

run_dlnm_casecross_ns(
  data = injury_cc,
  temp_var = "temp.mean",
  lag_days = 7,
  exp_probs = c(0.33,0.66)
)

```

#### Knots at (0.50,0.90) has the lowest AIC
